Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-04-11 paper/paper.tex
slightly better conclusion from the fine-tuned threshold experiment

% effects of extra training epochs and the impact of tau
We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
the compression and performance metrics before fine-tuning for various threshold levels
on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
the relative positions of the compression curves it can be concluded that $C$ has much
more substantial impact on the sparsity and performance, than the choice of $\tau$.
Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
downwards.

% (pending) threshold and fune-tuning? BETTER text
Bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} show improved performance
for thresholds below $-\tfrac12$ after fine-tuning. For higher $\tau$ the final stage
improves performance of a highly compressed model ($C=0.05$), while leaving moderately
compressed model ($C=0.005$) unaffected. This behaviour can be explained by the regularizing
effect of high compression rates, which servely reduce the excess degrees of freedom,
leaving less capacity for overfitting.
% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel

>>>>

% effects of extra training epochs and the impact of tau
We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
the compression and performance metrics before fine-tuning for various threshold levels
on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
the relative positions of the compression curves it can be concluded that $C$ has much
more substantial impact on the sparsity and performance, than the choice of $\tau$.
Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
downwards.
%
The bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} shows the effect of
the ``fine-tune'' stage: for $\tau \leq -1$ it improves the test performance, while leaving
it mostly unaffected for positive $\tau$. We attrbute this behaviour to regularization
effect of high compression rate, which limits the capacity for overfitting by significantly
reducing the excess degrees of freedom.
% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
